Weather Data Integration and Assimilation System\\

### 2020-02-15 method/sec_6-query.tex
Change all to \cref
Moved k8s to architectural decisions
Fixed:  workload
Grammarly Query

\section{Query Timeseries}

As described in Section \ref{subse:mongodb}, adapter-query is primarily using for support Geo-spatial queries. Other than that, as the primary service for searching for timeseries, it also supports for retrieval of timeseries metadata for external queries as well.

@@

QUERY\_STRING can be consist of zero to multiple parameters. Multiple query parameters are separated by the ampersand, "\&".
\begin{itemize}
    \item moduleId(Optional), e.g., HEC-HMS
    \item valueType(Optional), e.g., Scalar
    \item parameterId(Optional), e.g., O.Precipitation
    \item locationId(Optional), e.g., wdias\_hanwella
    \item timeseriesType(Optional), e.g., ExternalHistorical
    \item timeStepId(Optional), e.g., each\_15\_min
\end{itemize}
For the moment, query are only support by strict matching with above parameter values.

@@

\paragraph{Query Locations within Area}-- Using following API endpoint, it is possible to query the locations which are exists within the area provided by the geoJson data in the JSON payload.
\begin{lstlisting}
    POST <HOST_NAME>/query/location
    JSON Body:
    {
        "geoJson": {
            "type": "Polygon",
            "coordinates": [
                [
                    [
                        <longitude>,
                        <latitude>
                    ],
                    ...
                ]
            ]
        }
    }
\end{lstlisting}

paragraph{Query parameters in Locations}-- Using the following API endpoint, it is possible to query the parameters stored against given locations. Location IDs should be provide as list of JSON payload.
\begin{lstlisting}
    POST <HOST_NAME>/query/parameter
    JSON Body:
    ["<locationID>", ...]
\end{lstlisting}

>>>>

\section{Query Timeseries}
\label{se:query}

As described in \cref{subse:mongodb}, adapter-query is primarily using to support Geospatial queries. Other than that, as the primary service for searching for timeseries, it also supports for retrieval of timeseries metadata for external queries as well.

@@

QUERY\_STRING can be consist of zero to multiple parameters. Multiple query parameters are separated by the ampersand, "\&".
\begin{itemize}
    \item \texttt{moduleId} (Optional), e.g., HEC-HMS
    \item \texttt{valueType} (Optional), e.g., Scalar
    \item \texttt{parameterId} (Optional), e.g., O.Precipitation
    \item \texttt{locationId} (Optional), e.g., wdias\_hanwella
    \item \texttt{timeseriesType} (Optional), e.g., ExternalHistorical
    \item \texttt{timeStepId} (Optional), e.g., each\_15\_min
\end{itemize}
For the moment, query are only support by strict matching with above parameter values.

@@

\paragraph{Query Locations within Area}-- Using the following API endpoint, it is possible to query the locations which exist within the area provided by the GeoJson data in the JSON payload.
\begin{lstlisting}
    POST <HOST_NAME>/query/location
    JSON Body:
    {
        "geoJson": {
            "type": "Polygon",
            "coordinates": [
                [
                    [
                        <longitude>,
                        <latitude>
                    ],
                    ...
                ]
            ]
        }
    }
\end{lstlisting}

paragraph{Query parameters in Locations}-- Using the following API endpoint, it is possible to query the parameters stored against given locations. Location IDs should be provided as a list of JSON payload.
\begin{lstlisting}
    POST <HOST_NAME>/query/parameter
    JSON Body:
    ["<locationID>", ...]
\end{lstlisting}
